---
title: "How People Regards of Their Time in Children Caring"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    runtime: shiny
---

> Data source: CIA World Factbook (2017-01-10)

```{r setup, include=FALSE}

## IMPORT DATA & LIBRARY
library(flexdashboard)
require(tidyverse)
require(gridExtra)
require(readxl)
require(usmap)
require(tidycensus)
require(foreign) 
require(survey) 
require(readxl) 
require(rvest)

theme.info <- theme(plot.title = element_text(size=14, hjust=0.5),
                    axis.title = element_text(size=12),
                    axis.text=element_text(size=10)) 

total_participating <- read_excel("SeriesReport-20191128134937_8b2332.xlsx", skip=12)
man_participating <- read_excel("SeriesReport-20191128134958_5a9041.xlsx", skip=13)
woman_participating <- read_excel("SeriesReport-20191128135003_ca24da.xlsx", skip=12)
pew.data <- read.spss("Sep15 Parenting_clean.sav", to.data.frame=TRUE)
young_pop_pect_new <- read_csv("young_pop_pect.csv")
young_pop_pect_new$`Rank(total)`<-as.character(young_pop_pect_new$`Rank(total)`)

## Countries should be listed in the dropdown menu in alphabetical order.
young_pop_pect_new <-young_pop_pect_new[order(young_pop_pect_new$Country),]


## Since IP would be blocked, I save all data from this website to xlsx for using

# read_htlm() reads a webpage:

#young_population_percentage <- read_html("http://world.bymap.org/YoungPopulation.html")
#is.list(html_nodes(young_population_percentage, "table"))
#html_nodes(young_population_percentage, "table")[[1]]
#html_table(html_nodes(young_population_percentage, "table")[[1]], fill=TRUE)
# putting everything together:
#young_pop_pect <-  html_table(html_nodes(young_population_percentage, "table")[[1]], fill=TRUE)
#write.table (young_pop_pect, file ="young_pop_pect.xlsx", sep ="", row.names =FALSE, col.names =TRUE)

young_pop_pect_new <- young_pop_pect_new %>%
        rename("Young Generation Population Percentage" = `Total (percent)`,
               "Rank in Word" = `Rank(total)`) %>%
        select("Country","Young Generation Population Percentage","Rank in Word")



    
```


Row {data-height=600}
-----------------------------------------------------------------------
 

### {data-width=300}

Young Population (age under 15) Percentage of all Country in the World (2016)
```{r}

## Rename Rows
country.name <- young_pop_pect_new$Country
country.rank <- young_pop_pect_new$`Rank(total)`
country.percent <- young_pop_pect_new$`Total (percent)`

selectInput("Country", 
        label = "Choose a Country to display",
        choices = country.name,
        selected = "China")

## Out put table
       
renderTable(young_pop_pect_new%>%filter(country.name == input$Country))
    

```





-----------------------------------------------------------------------

### How People Regards of Their Time in Children Caring from Princeton Survey Research Associates at USA (2015) {data-width=400}


```{r}


## transfer data into tibble

pew.data <- as_tibble(pew.data) 

## setting up the survey design 

pew.design <- svydesign(ids=~1, 
                        weights=pew.data$utweight, 
                        data=pew.data)
# preparing data
time_allocation<-data.frame(round(svymean(~q12, design=pew.design), digits = 3))
# time_allocation

table5<-data.frame(time_allocation$mean)
row.names(table5) <- c("Too Much","Too Little","Right Amount","Don't know/Refused (VOL.)")


table5 <- table5 %>%
  as_tibble(rownames="response")

table5$response = factor(table5$response, levels=c("Right Amount","Too Little","Too Much","Don't know/Refused (VOL.)"))


## Bar Plot of Survey Result

table5 %>%
  mutate(
         percent = time_allocation.mean*100) %>%
  ggplot(aes(x=response, y=percent)) +
  geom_col(fill=c("paleturquoise4", "paleturquoise4", "paleturquoise4","paleturquoise4")) +
  ggtitle("How People Regards of Their Time in Children Caring") +
  labs(x="", y = "percent (%)")+
  theme(axis.text.x = element_text(angle = 30,hjust = 1,vjust = 1))+
  theme.info




```

> Data source: PEW RESEARCH CENTER; 2015 PARENTING SURVEY;Princeton Survey Research Associates International
> Note: (VOL.) for VOICEMAIL MESSAGE (LEAVE ONLY ONCE -- THE FIRST TIME A CALL GOES TO VOICEMAIL)


Row {data-height=600}
-----------------------------------------------------------------------
### {data-width=150}

```{r}

## Select Input button 
## Four options for selection

selectInput("varible", 
        label = "Choose a category to display",
        choices = c("Women and Men Combined" ="Total", "Men"="Man",
          "Women"="Woman","All Category"="All"),
        selected = "Total")


```

### Participating Percentage from 2007 to 2018 of USA {data-width=500}

```{r}

##  plot time series graph to the dashboard
renderPlot(
  if(input$varible == "Total"){
    
    total_participating %>% 
    ggplot(aes(x=Year, y=Estimate)) +
    geom_line() +
    geom_point() +
    ggtitle("Percent of Population Engaged in Activity (Caring for and helping household children under 18) on an Average Day") +
    scale_x_continuous(breaks =seq(2007, 2018, by=1), labels=seq(2007, 2018, by=1))+
    labs(y="Percentage") +
    theme.info

  }else if(input$varible == "Man"){
    
    man_participating %>% 
    ggplot(aes(x=Year, y=Estimate)) +
    geom_line() +
    geom_point() +
    ggtitle("Percent of Population Engaged in Activity (Caring for and helping household children under 18) on an Average Day (Man)") +
    scale_x_continuous(breaks =seq(2007, 2018, by=1), labels=seq(2007, 2018, by=1))+
    labs(y="Percentage") +
    theme.info
  }else if(input$varible == "Woman"){
    
    woman_participating %>% 
    ggplot(aes(x=Year, y=Estimate)) +
    geom_line() +
    geom_point() +
    ggtitle("Percent of Population Engaged in Activit (Caring for and helping household children under 18) on an Average Day (Woman)") +
    scale_x_continuous(breaks =seq(2007, 2018, by=1), labels=seq(2007, 2018, by=1))+
    labs(y="Percentage") +
    theme.info

  }else{

    total_data <- left_join(total_participating,man_participating , by="Year")
    total_data <- left_join(total_data, woman_participating,by="Year")
    total_data <- total_data %>%
    rename(Total = `Estimate.x`,
         Men = `Estimate.y`,
         Women = `Estimate`)


    total_data %>% 
  ggplot() +
  geom_line(aes(x = Year,y = Total,colour = "Total")) +
  geom_line(aes(x = Year,y = Women,colour = "Women"))+
  geom_line(aes(x = Year,y = Men,colour = "Men"))+
  geom_point(aes(x = Year,y = Total,colour = "Total")) +
  geom_point(aes(x = Year,y = Women,colour = "Women"))+
  geom_point(aes(x = Year,y = Men,colour = "Men"))+
  ggtitle("Percent of Population Engaged in Activity (Caring for and helping household children under 18) on an Average Day ") +
  scale_x_continuous(breaks =seq(2007, 2018, by=1), labels=seq(2007, 2018, by=1))+
  labs(y="Percentage") +
      guides(color=guide_legend(title=NULL)) +
  theme.info
  }
    ) # end line code

```

> Data source: American Time Use; Percent of population engaged in activity on an average day (2008 to 2018)







